Text Is All You Need

### 2023-05-11 docs/hes_final/presentation.qmd
move ffnn context features to speaker notes

## Additional country context inputs

- 2 numerical indicators from UNICEF's State of the World's Children report: 
  + 'Under-five mortality rate 2019' 
  + 'Adolescent population 2020 Proportion of total population (%) Total'
- 3 one-hot-encoded categorical indicators: 
  + Human Development Index ranges 
  + gross national income per capita
  + Fragile States Index ranges

:::{.notes}
- avoid the per-country 'small data problem' by allowing model to learn similarities between country contexts and generalize
:::

@@

>>>>

@@

:::{.notes}
- avoid the per-country 'small data problem' by allowing model to learn similarities between country contexts and generalize
- 2 numerical indicators from UNICEF's State of the World's Children report: 
  + 'Under-five mortality rate 2019' 
  + 'Adolescent population 2020 Proportion of total population (%) Total'
- 3 one-hot-encoded categorical indicators: 
  + Human Development Index ranges 
  + gross national income per capita
  + Fragile States Index ranges
:::
